Software reliability: Experiences\\ in European scientific research\\ projects and new trends

### 2017-11-09 paper.tex
remove cite

The ETICS and ETICS 2 (2006 -- 2010) \cite{cordis:etics} projects aimed at defining and implementing a framework able to integrate a combination of new technologies in test management, release management tools and resource virtualization to improve quality, reliability and interoperability of large--scale scientific software. Both projects supported mechanisms to measure static software metrics, number of faults, number of defects and number of bugs; execute unit testing; deploy and test software on a virtual set of resources \cite{etics}. The {\sl ETICS} portal was the first automated service for delivering software products in distributed environments such as the Grid.

>>>>

The ETICS and ETICS 2 (2006 -- 2010) \cite{cordis:etics} projects aimed at defining and implementing a framework able to integrate a combination of new technologies in test management, release management tools and resource virtualization to improve quality, reliability and interoperability of large--scale scientific software. Both projects supported mechanisms to measure static software metrics, number of faults, number of defects and number of bugs; execute unit testing; deploy and test software on a virtual set of resources. The {\sl ETICS} portal was the first automated service for delivering software products in distributed environments such as the Grid.
